### 2024-05-31 README.Rmd
fix broken links in top-level README

Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).
For more information about how tracking worked, Go to the [Open science workflow tab](https://stefanvermeent.github.io/abcd_ddm/opensci_workflow/README.html).

@@

# Print milestones
glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        - **Data MD5 hash**: {hash}
        - [Link to code snippet](https://github.com/StefanVermeent/liss_wm_profiles_2023/blob/{branch}/.projectlog/{commit}.R)
        \n
    ")

@@

1.  [Pilot preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/1_pilot/scripts/0_data_prep).
2.  [Study 1 preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/2_study1/scripts/0_data_prep).
3.  [Study 2 preprocessing scripts](https://github.com/stefanvermeent/attention_project/blob/main/3_study2/scripts/0_data_prep).

>>>>

Below is an overview of all the project milestones (e.g., timestamped versions of the preregistrations).
Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).
Clicking the link of a specific milestone will take you to the historic version of the repository (i.e., as it was when the milestone was timestamped).

@@

# Print milestones
glue_data(milestones, "  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        \n
    ")

@@

1.  [Pilot preprocessing scripts](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/1_pilot/scripts/0_data_prep).
2.  [Study 1 preprocessing scripts](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/2_study1/scripts/0_data_prep).
3.  [Study 2 preprocessing scripts](https://github.com/stefanvermeent/attention_project/tree/main/preregistrations/3_study2/scripts/0_data_prep).
